Staged Abstract Interpreters

### 2019-02-04 paper/60_eval.tex
reorganize and address typos

To evaluate the performance can be improved through staging, we use the abstract
interpreter demonstrated in the paper to analyze some Scheme programs. We first implement
a desugaring transformation for a large subset of scheme that transforms into the
small language we used in the paper.
We use the same generic interface with a 0-CFA-like abstraction, and the unstage abstract
interpreter forms the baseline.

@@

\subsection{Benchmarks}
The benchmark programs we used are collected from previous papers \cite{Johnson:2013:OAA:2500365.2500604,
ashley:practical, DBLP:journals/corr/abs-1102-3676} and exisiting artifacts \footnote{https://github.com/ilyasergey/reachability}.

We used the following benchmark programs:
\begin{itemize}
    \item \textbf{fib}: Calculates the $n$-th fibonacci number.
    \item \textbf{rsa}: The RSA public key encryption algorithm.
    \item \textbf{kcfa3}: A difficult benchmark for $k$-CFA.
    \item \textbf{church}: Church numerals with additions and mutiplications.
    \item \textbf{fermat}: Fermat and Solovay-Strassen primality testing.
    \item \textbf{kcfa-worst-case-}\textit{n}: 
      Benchmark programs that are supposed to be tough cases for $k$-CFA; 
      the number $n$ indicates the depth of nesting lambda terms.
\end{itemize}

@@

As we can see from the table, the staged version significantly outperforms the unstaged especially 
for the difficult ones.
However, for some benchmarks, we observe degraded performance. 
We conjecture this happens due to the large size of the generated code is unoptimized -- 
as what we test here is a simple implementation almost identical to what we described in the previous sections,
we believe the performance still can be improved if more engineering effort is taken, 
such as optimizing code generation and avoiding code duplication.

>>>>

To evaluate whether the performance can be improved through staging, we use the
abstract interpreter demonstrated in the paper to analyze some Scheme programs.
We first implement a desugaring transformation for a large subset of Scheme that
transforms into the small language we used in the paper. We use the same generic
interface with a 0-CFA-like abstraction, and the unstage abstract interpreter
forms the baseline.

@@

\subsection{Benchmarks}

The benchmark programs we used are collected from previous papers
\cite{Johnson:2013:OAA:2500365.2500604, ashley:practical,
DBLP:journals/corr/abs-1102-3676} and exisiting artifacts
\footnote{https://github.com/ilyasergey/reachability}.

We used the following benchmark programs:

\begin{itemize}
    \item \textbf{fib}: Calculates the $n$-th fibonacci number.
    \item \textbf{rsa}: The RSA public key encryption algorithm.
    \item \textbf{kcfa3}: A difficult benchmark for $k$-CFA.
    \item \textbf{church}: Church numerals with additions and mutiplications.
    \item \textbf{fermat}: Fermat and Solovay-Strassen primality testing.
    \item \textbf{kcfa-worst-case-}\textit{n}: 
      Benchmark programs that are supposed to be tough cases for $k$-CFA; 
      the number $n$ indicates the depth of nesting lambda terms.
\end{itemize}

@@

As we can see from the table, the staged version significantly outperforms the
unstaged especially for the difficult ones. However, for some benchmarks, we
observe degraded performance. We conjecture this happens due to the fact that
the large size of the generated code is unoptimized -- as what we test here is a
simple implementation almost identical to what we described in the previous
sections, we believe the performance still can be improved if more engineering
effort is taken, such as optimizing code generation and avoiding code
duplication.
